\papertitle

### 2025-03-21 src/tex/ms.tex
[showyourwork] overleaf sync

The approach outlined above provides the average position in a two-dimensional coordinate system, and then projects this onto a position on the circle corresponding to a position in periodic space (\cref{fig:method_comparison}c). 
However, this projection is from a non-physically meaningful position, i.e., the position does not sit on the manifold of the circle itself.
The result of using a position on the plane of the circle, rather than the circle itself, is a discrepancy when comparing the circular weighted average centre of mass with that of the system in a non-periodic space.

>>>>

The approach outlined above provides the average position in a two-dimensional coordinate system, and then projects this onto a position on the circle corresponding to a position in periodic space (\cref{fig:method_comparison}c). 
However, this projection is from a position with no physical meaning in the context of the periodic cell, i.e., the position does not sit on the manifold of the circle itself.
The result of using a position on the plane of the circle, rather than the circle itself, is a discrepancy when comparing the circular weighted average centre of mass with that of the system in a non-periodic space.
